Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2015-01-12 misc/SI_thesis.tex
vls vss paper reading

\chapter{moo3}
\ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed. This is caused by the fact that four of the six surrounding O atom are at distances from 1.67 \si{\angstrom} to 1.95 \si{\angstrom}, while the remaining two are as far as 2.25 and 2.33 \si{\angstrom}. This also stress that the \ce{MOO6} octahedra are rather distorted.

>>>>

\chapter{moo3}

molybdena, mobility of the hexavalent \ce{Mo6+} ions in MoO3 modified by Na+, \cite{El-Shobaky1998} Solid-solid reaction between \ce{Na2O} and \ce{MoO3}: 
\[
\cee{Na2O + 2MoO3 \rightarrow[500 C] Na2Mo2O7}
\]
The solubility of sodium oxide in \ce{MoO3} lattices is controlled by the chemical affinity towards the formation of \ce{Na2Mo2O7}. Other phases, such as \ce{Na2Mo3O8}, \ce{Na2Mo3O4} were detected by XRD.

MoO3 spreading on \ce{Al2O3}: solid-solid wetting process, favored by the decrease of total surface energy. 800 K heating, gas phase transport ruled out.\cite{Leyrer1990} 
\[
\Delta F = \gamma_M - \gamma_S + \gamma_{MS}
\]
where the subscript M, S denote material and substrate, respectively.
solid state reaction between MoO3 and Al2O3 can occur, resulting \ce{Al2(MoO4)3}, while reaction between MoO3 and \ce{SiO2} is not reported.

MoO3 on Au (111).\cite{Song2003} spreading phase as molten MoO3. surface free energy of \ce{Al2O3} as , \ce{MoO3} as .

crystal anisotropy affect the morphology and growth direction. \cite{Schwarz2009} \cite{Schwarz2010}

\cite{Dubrovskii2011}

\cite{Cao2012a}

\cite{Shin2012}

\cite{Rathi2013}

Si NW growth using Au and SiH4, the growth species incorporation rate into liquid appears larger than that into solid because of the catalytic reaction on the metal, not of the rough surface of liquid phase. The catalytic particles can lower the barrier that is present on the particle-solid interface as compared to that on the vapor-solid interface. As to the catalytic particle being liquid \cite{Harmand2005, Park2006} or solid \cite{Dick2005,Persson2004}, results from the growth of III-V NWs using different catalysts indicate it barely matter. \cite{Kolasinski2006} And the phase from which the growth material is taken is of little consequence. The essential role of catalyst appears to be in lowering the activation energy of nucleation at the growth interface.

Cu-Si NW, VSS mechanism, in-situ TEM, \cite{Wen2009} Si growth direction show multiple ones instead of the major 111 direction in VLS method. solid catalyst be advantageous in fabricating heterostructure due to the low solubility of growth species in solid.

ZnO NW by AuZn alloy, VSS occurs via a solid diffusion mechanism.\cite{Campos2008} the low-temperature growth of ZnO nanowires from solid Au–Zn catalysts as being an intermediate between the VLS and VS processes. The presence of a low-energy epitaxial interface between solid catalyst and the NW will favor NW growth.

Size effect evaluated by cohesive energy theory.\cite{Qi2005} $T = T_b (1 - N/2n)$, where N surface atoms and n total atoms.

\begin{table}[htb]
\centering
\caption{melting of nanosolids}\label{tab:nano}
\begin{tabular}{ccp{2in}}
\toprule
Morphology & N/n &  Remarks   \\
\midrule
sphere     &  4d/D  & d atom diameter, D sphere diameter   \\ 
disk-like     &  4d(1/3h+ 2/3l)  & d atom diameter, l disk diameter, h disk height \\ 
nanowire     &  8d/3l & d atom diameter, l wire diameter   \\ 
\bottomrule
\end{tabular}
Note: atomic diameter calculated by atomic volume per mole.
\end{table}

For example, the atomic weight of Pb is 207 g/mol, and density is 11.34 g/cm3; then the molar volume is 207/11.34 = 18.2539. Assuming sphere as building unit, then $\frac{\pi}{6}D^3$ = 18.2539/N_A. Solving D as 0.3868 nm.

for \ce{MoO3}, d as 0.46 nm.

catalyst acts as a sink for Zn, generating concentration gradient. growth rate and diffusion coefficient estimation, MoO3 diffusing in liquid should be faster than in solid, this can explain the longer dimension in the length of belts than the height of towers. open issue, 
Na2MoO4-MoO3 phase diagram indicates that for T less than 500 C, the Na-Mo-O alloy will remain solid for all MoO3 concentration.

\ce{MoO3}, an alternative interpretation in terms of tetrahedral coordination of Mo atoms is also proposed. This is caused by the fact that four of the six surrounding O atom are at distances from 1.67 \si{\angstrom} to 1.95 \si{\angstrom}, while the remaining two are as far as 2.25 and 2.33 \si{\angstrom}. This also stress that the \ce{MoO6} octahedra are rather distorted.
